### 2021-02-21 architecture.tex
Remove an empty line
Describe output layer

\subsection{Projection: From symbol embeddings to symbol costs}

>>>>

\subsection{Output layer: From symbol embeddings to symbol costs}

The symbol cost of each symbol is computed by passing the symbol's embedding through a dense layer with a single output unit.
No activation function is applied so that the output values can span the whole $\re$.

Note that it is possible to use a more complex projection module,
e.g., a feed-forward network with one or more hidden layers.
\todo{FB: Ensure the term is defined.}
Our experiments showed no significant improvement when a hidden layer is added,
arguably because the underlying \gls{gcn} learns a sufficiently complex transformation.

For input problem $P$
with signature $\Sigma = (s_1, \ldots, s_n)$,
we denote the cost of the $i$-th symbol as $c(i)$.
